The \dealii{} Library, Version 9.0

### 2018-04-04 9.0/paper.tex
Add list of major changes.

\author[4]{Timo Heister}
\affil[4]{Mathematical Sciences,
  O-110 Martin Hall,
  Clemson University,
  Clemson, SC 29634, USA.
  {\texttt{heister@clemson.edu}}}
% 
% \author[5]{Luca Heltai}
% \affil[5]{SISSA,
%   International School for Advanced Studies,
%   Via Bonomea 265,
%   34136, Trieste, Italy.
% {\texttt{luca.heltai@sissa.it}}}
% 
% \author[6]{Martin Kronbichler}
% \affil[6]{Institute for Computational Mechanics,
%   Technical University of Munich,
%   Boltzmannstr.~15, 85748 Garching, Germany.
%   {\texttt{kronbichler@lnm.mw.tum.de}}}
% 
\author[7]{Matthias Maier}
\affil[7]{School of Mathematics,
  University of Minnesota,
  127 Vincent Hall, 206 Church Street SE,
  Minneapolis, MN 55455, USA.
  {\texttt{msmaier@umn.edu}}}
% 
% \author[8]{Jean-Paul Pelteret}
% \affil[8]{Chair of Applied Mechanics,
%   University of Erlangen-Nuremberg,
%   Egerlandstr.\ 5,
%   91058 Erlangen,
%   Germany.
%   {\texttt{jean-paul.pelteret@fau.de}}}
% 
% \author[9]{Bruno Turcksin\footnote{
%   This manuscript has been authored by UT-Battelle, LLC under Contract No.
%   DE-AC05-00OR22725 with the U.S. Department of Energy. The United States
%   Government retains and the publisher, by accepting the article for
%   publication, acknowledges that the United States Government retains a
%   non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce
%   the published form of this manuscript, or allow others to do so, for United
%   States Government purposes. The Department of Energy will provide public
%   access to these results of federally sponsored research in accordance with the
%   DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}}
% \affil[9]{Computational Engineering and Energy Sciences Group,
%   Computional Sciences and Engineering Division,
%   Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
%   TN 37831, USA.
%   {\texttt{turcksinbr@ornl.gov}}}
% 
% \author[10]{David Wells}
% \affil[10]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
% Troy, NY 12180, USA.
%   {\texttt{wellsd2@rpi.edu}}}

@@

@@

\item New tutorial programs XYZ; as well as
  updates to XYZ. In addition, the separate code
  gallery of \dealii{} has gained a number of new entries.

  \item More than XYZ other features and bugfixes.
\end{itemize}
The more important ones of these changes will be detailed in the
following section.  Information on how to cite \dealii{} is provided
in Section \ref{sec:cite}.

>>>>

\author[4]{Timo Heister}
\affil[4]{Mathematical Sciences,
  O-110 Martin Hall,
  Clemson University,
  Clemson, SC 29634, USA.
  {\texttt{heister@clemson.edu}}}
% 
% \author[5]{Luca Heltai}
% \affil[5]{SISSA,
%   International School for Advanced Studies,
%   Via Bonomea 265,
%   34136, Trieste, Italy.
% {\texttt{luca.heltai@sissa.it}}}
% 
% \author[6]{Martin Kronbichler}
% \affil[6]{Institute for Computational Mechanics,
%   Technical University of Munich,
%   Boltzmannstr.~15, 85748 Garching, Germany.
%   {\texttt{kronbichler@lnm.mw.tum.de}}}
% 
\author[7]{Matthias Maier}
\affil[7]{School of Mathematics,
  University of Minnesota,
  127 Vincent Hall, 206 Church Street SE,
  Minneapolis, MN 55455, USA.
  {\texttt{msmaier@umn.edu}}}
% 
% \author[8]{Jean-Paul Pelteret}
% \affil[8]{Chair of Applied Mechanics,
%   University of Erlangen-Nuremberg,
%   Egerlandstr.\ 5,
%   91058 Erlangen,
%   Germany.
%   {\texttt{jean-paul.pelteret@fau.de}}}
% 
 \author[9]{Bruno Turcksin\footnote{
   This manuscript has been authored by UT-Battelle, LLC under Contract No.
   DE-AC05-00OR22725 with the U.S. Department of Energy. The United States
   Government retains and the publisher, by accepting the article for
   publication, acknowledges that the United States Government retains a
   non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce
   the published form of this manuscript, or allow others to do so, for United
   States Government purposes. The Department of Energy will provide public
   access to these results of federally sponsored research in accordance with the
   DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}}
 \affil[9]{Computational Engineering and Energy Sciences Group,
   Computional Sciences and Engineering Division,
   Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
   TN 37831, USA.
   {\texttt{turcksinbr@ornl.gov}}}
% 
% \author[10]{David Wells}
% \affil[10]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
% Troy, NY 12180, USA.
%   {\texttt{wellsd2@rpi.edu}}}

@@

\item 
  Support for GPU

\item
  Increase support for dense solvers (LAPACK changes and new ScaLAPACK
  interface).

\item
  Support for Sundials

\item 
  Support for Particles

\item 
  Support for automatically differentiable numbers

\item 
  Support for complex-values vectors is now at the same level as real-valued
  vectors.

@@

\item New python tutorial program tutorial-1; as well as
  updates to step-37. In addition, the separate code
  gallery of \dealii{} has gained a number of new entries.

  \item More than 330 other features and bugfixes.
\end{itemize}
The more important ones of these changes will be detailed in the
following section.  Information on how to cite \dealii{} is provided
in Section \ref{sec:cite}.
